%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{\Large Pavanpreet Singh Gandhi} & Email : \href{mailto:pavanpreet.gandhi@gmail.com}{pavanpreet.gandhi@gmail.com}\\
    \href{https://pavanpreet-gandhi.github.io/}{Website},
    \href{https://www.linkedin.com/in/pavanpreet-gandhi/}{LinkedIn}, 
    \href{https://github.com/pavanpreet-gandhi}{GitHub} & Mobile : +44 (0)7927 658364 \\
\end{tabular*}


%-----------SKILLS-----------------
\section{Skills}
\resumeSubHeadingListStart
    \resumeSubItem{Programming Languages}
    {Python, R, SQL, Bash}
    \resumeSubItem{Programming Frameworks}
    {PyTorch, JAX, HuggingFace, NumPy, Pandas, Matplotlib, etc.}
    \resumeSubItem{Technologies}
    {Deep Learning, Large Language Models, Reinforcement Learning, Probabalsitic Modelling, Gaussian Processes, Bayesian Inference, Time Series Analysis, Anomaly Detection}
    \resumeSubItem{Tools}
    {Git, Docker, Linux, Jupyter Notebooks, Streamlit}
\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {American Express}{Brighton, UK}
      {Graduate Data Scientist}{Sep 2023 -- Aug 2024}
      \resumeItemListStart
        \resumeItem{Anomaly Detection}
          {Applied \textbf{unsupervised learning} techniques and \textbf{robust statistics} to detect anomalies in call-volume data. Deployed the model in a system to automatically send alerts to the operations teams.}
        \resumeItem{Data Engineering}
          {Maintained \textbf{PySpark} data pipelines and developed a custom uploader-factory system enabling 200+ non-technical users to upload data directly to the data lake.}
        \resumeItem{Data Science Community}
          {Part of the organising community for a 100+ member data science community. Presented a talk on software engineering best practices for data science.}
      \resumeItemListEnd

    \resumeSubheading
      {American Express}{Brighton, UK}
      {Data Science Internship}{Jun 2022 -- Aug 2022}
      \resumeItemListStart
        \resumeItem{Time Series Forecasting}
        {Developed a \textbf{time series forecasting model} leveraging Prophet and NeuralProphet to predict call volumes over various time horizons.}
        \resumeItem{UX Research}
          {Met with multiple stakeholders accross the business to understand their needs and pain points.}
      \resumeItemListEnd

    \resumeSubheading
      {Looloo Technology}{Bangkok, Thailand}
      {Machine Learning Internship}{Jul 2021 -- Dec 2021}
      \resumeItemListStart
        \resumeItem{Underline Detection}
          {Developed a novel \textbf{computer vision} algorithm based on \textbf{Gabor filters} to detect and remove underlines from handwritten text.}
        \resumeItem{Auction Price Prediction}
          {Continued working part-time on \textbf{feature engineering} of confidential order-book data for a \textbf{reinforcement learning} algorithm that predicts the auction price of a stock.}
      \resumeItemListEnd
    
    \resumeSubheading
      {Mahidol University}{Bangkok, Thailand}
      {TA and Tutor}{Jan 2021 -- Dec 2021}
      \resumeItemListStart
        \resumeItem{Discrete Maths TA}
          {Teacher assistant for course taught by Dr Piti Ongmongkolkul.}
        \resumeItem{Maths Clinic Tutor}
          {Helped students struggling with first-year undergraduate maths courses.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education}
    \resumeSubHeadingListStart
        \resumeSubheading
            {University College London}{London, UK}
            {Master of Science in Computational Statistics and Machine Learning}{Aug 2024 -- Present}
            \resumeItemListStart
                \resumeItem{Relevant Courses}
                  {Reinforcement Learning (DeepMind), 
                  Open-Endedness and General Intelligence (Tim Rocktäschel et al.), 
                  Probabalsitic Unsupervised Learning (Gatsby).
                  % Machine Learning Seminar, 
                  % Bayesian Deep Learning, 
                  % Satatistical Models and Data Analysis, 
                  % Supervised Learning, 
                  % Applied Deep Learning.
                  }
                \resumeItem{Thesis}
                  {Working with Century Tech on \textbf{audio reasoning models} for 
                  automated grading of oral assessments.}
            \resumeItemListEnd
        \resumeSubheading
            {Mahidol University International College}{Bangkok, Thailand}
            {Bachelor of Science in Applied Mathematics; GPA: 3.89}{Aug 2019 -- Apr 2023}
            \resumeItemListStart
                \resumeItem{Relevant Courses}
                  {Deep learning, Machine Learning, Optimization, Numerical Methods.}
                \resumeItem{Thesis}
                  {Deep Q-Learning for Stock Portfolio Optimization.}
            \resumeItemListEnd
        \resumeSubheading{NIST International School}{Bangkok, Thailand}
        {IB Diploma}{Aug 2017 -- Jun 2019}
        \resumeSubheading{NPS International School}{Singapore}
        {IGCSE}{Aug 2008 -- Jun 2017}
    \resumeSubHeadingListEnd


% %-----------PROJECTS-----------------
% \section{Projects}
%   \resumeSubHeadingListStart
%     \resumeSubItem{QuantSoftware Toolkit}
%       {Open source python library for financial data analysis and machine learning for finance.}
%     \resumeSubItem{Github Visualization}
%       {Data Visualization of Git Log data using D3 to analyze project trends over time.}
%     \resumeSubItem{Recommendation System}
%       {Music and Movie recommender systems using collaborative filtering on public datasets.}
% %     \resumeSubItem{Mac Setup}
% %       {Book that gives step by step instructions on setting up developer environment on Mac OS.}
%   \resumeSubHeadingListEnd

%

%-------------------------------------------
\end{document}